Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-14 manuscript/main.tex
cross covariance functional compact

	\subsection{Tucker's Criterion}\jongmin{notation not yet changed}
	We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}. We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
	\begin{equation}\label{def:cross_covariance_yx}
\sigma_{YX}
 (\sigma_{YX, 1} , \ldots, \sigma_{YX, K} )
[Y_1 X_{11}]
,\ldots, 
[Y_1  X_{1K}]
\bigr)   \in \mathcal{F}^{\otimes K},
and between the response and the scalar predictor:
\sigma_{YZ} 
(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
\mathbb{E}[Y_1 Z_{11}]
,\ldots,
\mathbb{E}[Y_1 Z_{1p}]
\bigr)^\top %= E(Y\mathbf{Z})
\in \mathbb{R}^p.
Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
\Sigma_{YW} :=  
[ Y_1 W_1 ]
\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
\bigr) \in \mathcal{H}.
Based on these definitions, we introduce two cross-covariance operators.
\begin{lemma}\label{lemma:cross_cov_operator}
Define $\mathcal{C}_{YW}= \mathbb{E}(W_1 \otimes_\mathcal{H} Y_1): \mathcal{H} \rightarrow \mathbb{R}$,
which	maps  
	$h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ to a real number:
		\mathcal{C}_{YW}
		h
		\bigl[ 
		\bigr] 
		\langle \Sigma_{YW}, h \rangle_\mathcal{H}
		\sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt 
		\sigma_{YW}^\top \mathbf{v}.
	Next, define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$,
which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
		\mathcal{C}_{WY} d 
		\bigl[
		\langle Y_1, d \rangle W_1 
		\bigr] 
		[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
\end{lemma}
The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
Based on these two operators, we define a positive   operator as follows:
\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
Define
	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ as an operator which performs the following mapping:
		\mathcal{U} h 
		\mathcal{C}_{WY} ( \mathcal{C}_{YW} h) 
		\mathcal{C}_{YW} (\langle \Sigma_{YW}, h \rangle_\mathcal{H}) 
		\Sigma_{YW} \, \langle \Sigma_{YW}, h \rangle_\mathcal{H} 
		(\Sigma_{YW} \otimes \Sigma_{YW}) h.
		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
		Then $\mathcal{U}$
	 is self-adjoint and positive-semidefinite.
\end{lemma}
The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
To guarantee the existence of a complete orthonormal system of eigenfunctions for $\mathcal{U}$ in $\mathcal{H}$, we  first demonstrate that $\mathcal{U}$ is  a compact operator,
that is,
images of a bounded sequence contains a convergent subsequence (for a formal definition, see Definition 4.1.1 of \citealt{hsingTheoreticalFoundationsFunctional2015}).
To this end, we begin by defining the notion of uniform continuity for the cross-covariance function defined in \eqref{def:cross_covariance_yx}:
\begin{definition}[Uniform Continuity]\label{def:uniform_continuity}
	For each $k \in \{1, \ldots, K\}$, the cross-covariance function $\sigma_{YX, k} \in \mathcal{F}$ is uniformly continuous if for any $\epsilon > 0$, there exists a $\delta_k > 0$ such that for all $t_1, t_2 \in [0,1]$ satisfying $|t_1 - t_2 | < \delta_k$, we have
		| \sigma_{YX, k} (t_1) - \sigma_{YX, k} (t_2) | < \epsilon.
\end{definition}
Using this definition, the following proposition states that $\mathcal{U}$ is a compact operator under a mild condition.
	\begin{proposition}[Compactness condition] \label{proposition:compact_operator}
If there exist finite constants $Q_1$ and $Q_2$ such that
		\begin{align}\label{condition_for_compact}
			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
		\end{align}
		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous,
		then $\mathcal{U}$ is a compact operator.
\end{proposition}
The proof of Proposition \ref{proposition:compact_operator} is provided in Appendix \ref{section:proof:proposition:compact_operator}.
	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Proposition \ref{proposition:compact_operator} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
\begin{theorem}[Population PLS]\label{proposition: eigenanalysis} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
	\begin{equation*} 
		\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathcal{H}, Y \right)
		\end{equation*} 
	is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
\end{theorem}
	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.

@@

@@

\section{Proof of Proposition \ref{proposition: eigenanalysis}}\label{section:proof:proposition: eigenanalysis}

	\noindent Now we prove Proposition \ref{proposition: eigenanalysis}. The singular value decomposition of $\mathcal{C}_{YW}$ is given by
	\begin{equation*}
		\mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
	\end{equation*}
	Let $\Vert \cdot \Vert_{op}$ denote an operator norm. Then, applying Theorem 4.3.4 in \citet{hsingTheoreticalFoundationsFunctional2015}, we can show that
	\begin{equation*}
		\Vert \mathcal{C}_{YW} \Vert_{op} = \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} | \mathcal{C}_{YW} \mathbf{h} |^2 
		= \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} | E(\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y)|^2 
		= \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} \textnormal{Cov}^2(\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H}, Y) 
		= \kappa_1^2,
	\end{equation*}
	with maximum attained at $\mathbf{h}=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \, \circ \, \mathcal{C}_{YW} = \mathcal{C}_{WY} \, \circ \, \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\kappa_1^2.$

>>>>

	\subsection{Tucker's Criterion}\jongmin{notation not yet changed}
	We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}. We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
	\begin{equation}\label{def:cross_covariance_yx}
\sigma_{YX}
=
 \bigl(
 \sigma_{YX, 1}(t) , \ldots, \sigma_{YX, K}(t) 
 \bigr)
  :=
\bigl(
\mathbb{E}
[Y_1 X_{11}]
,\ldots, 
\mathbb{E}
[Y_1  X_{1K}]
\bigr)   \in \mathcal{F}^{\otimes K},
	\end{equation}
and between the response and the scalar predictor:
\begin{equation*}
\sigma_{YZ} 
= 
(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
:= 
\bigl(
\mathbb{E}[Y_1 Z_{11}]
,\ldots,
\mathbb{E}[Y_1 Z_{1p}]
\bigr)^\top %= E(Y\mathbf{Z})
\in \mathbb{R}^p.
\end{equation*}
Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
\begin{equation*}
\Sigma_{YW} :=  
\mathbb{E}
[ Y_1 W_1 ]
=
\bigl(
\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
\bigr) \in \mathcal{H}.
\end{equation*}
Based on these definitions, we introduce two cross-covariance operators.
\begin{lemma}\label{lemma:cross_cov_functional}
Define the operator $
\mathcal{C}_{YW}
=
\mathbb{E}(W_1 \otimes_\mathcal{H} Y_1)
: \mathcal{H} \rightarrow \mathbb{R}$ such that for any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$, it maps $h$ to a real number as: \begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W_1, h \rangle_\mathcal{H} Y_1 \right] = \langle \Sigma_{YW}, h \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt + \sigma_{YW}^\top \mathbf{v}. \end{equation*} 
If there exist finite constants $Q_1$ and $Q_2$ such that
\begin{align}\label{condition_for_compact}
	\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
\end{align}
the operator $\mathcal{C}_{YW}$ is a compact operator.
\end{lemma}
Proof of Lemma \ref{lemma:cross_cov_functional}
is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
\begin{lemma}\label{lemma:cross_cov_operator}
Define $\mathcal{C}_{YW}= : \mathcal{H} \rightarrow \mathbb{R}$,
which	maps  
	$h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathcal{H}$ to a real number:
	\begin{equation*}
		\mathcal{C}_{YW}
		h
		:=
		\mathbb{E} 
		\bigl[ 
		\langle W_1, h \rangle_\mathcal{H} Y_1 
		\bigr] 
		= 
		\langle \Sigma_{YW}, h \rangle_\mathcal{H}
		=
		\sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt 
		+ 
		\sigma_{YW}^\top \mathbf{v}.
	\end{equation*}
	Next, define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathcal{H}$,
which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathcal{H}$ as follows:
	%%%%
	\begin{align*}		
		\mathcal{C}_{WY} d 
		:= 
		\mathbb{E} 
		\bigl[
		\langle Y_1, d \rangle W_1 
		\bigr] 
		= 
		\mathbb{E}
		[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
	\end{align*}
Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
\end{lemma}

The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.
Based on these two operators, we define a positive   operator as follows:
\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
Define
	$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ as an operator which performs the following mapping:
	\begin{equation*}
		\mathcal{U} h 
		= 
		\mathcal{C}_{WY} ( \mathcal{C}_{YW} h) 
		=
		\mathcal{C}_{YW} (\langle \Sigma_{YW}, h \rangle_\mathcal{H}) 
		=  
		\Sigma_{YW} \, \langle \Sigma_{YW}, h \rangle_\mathcal{H} 
		= 
		(\Sigma_{YW} \otimes \Sigma_{YW}) h.
	\end{equation*}
		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
		Then $\mathcal{U}$
	 is self-adjoint and positive-semidefinite.
\end{lemma}
The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.

The fundamental property of classical scalar PLS is that the first eigenvector of the squared covariance matrix corresponds to the first PLS component direction. To derive an analogous result in the hybrid regression setting, we first demonstrate that $\mathcal{U}$ is a compact operator. This means that the image of any bounded sequence under $\mathcal{U}$ contains a convergent subsequence (for a formal definition, see Definition 4.1.1 of \citealt{hsingTheoreticalFoundationsFunctional2015}). The compactness of $\mathcal{U}$ is crucial as it guarantees the existence of a complete orthonormal system of eigenfunctions for $\mathcal{U}$ in $\mathcal{H}$.
To this end, we begin by defining the notion of uniform continuity for the cross-covariance function defined in \eqref{def:cross_covariance_yx}:
\begin{definition}[Uniform continuity]\label{def:uniform_continuity}
	For each $k \in \{1, \ldots, K\}$, the cross-covariance function $\sigma_{YX, k} \in \mathcal{F}$ is uniformly continuous if for any $\epsilon > 0$, there exists a $\delta_k > 0$ such that for all $t_1, t_2 \in [0,1]$ satisfying $|t_1 - t_2 | < \delta_k$, we have
$
		| \sigma_{YX, k} (t_1) - \sigma_{YX, k} (t_2) | < \epsilon.
$
\end{definition}
Using this definition, the following proposition states that $\mathcal{U}$ is a compact operator under a mild condition.
	\begin{proposition}[Compactness condition] \label{proposition:compact_operator}

		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous,
		then $\mathcal{U}$ is a compact operator.
\end{proposition}
The proof of Proposition \ref{proposition:compact_operator} is provided in Appendix \ref{section:proof:proposition:compact_operator}.
	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Proposition \ref{proposition:compact_operator} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
\begin{theorem}[Population PLS]\label{theorem:population_PLS} Under the conditions of Proposition \ref{proposition:compact_operator}, the constrained maximum
	\begin{equation*} 
		\max \limits_{\substack{\xi \in \mathcal{H} \\ \Vert \xi \Vert_\mathcal{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathcal{H}, Y \right)
		\end{equation*} 
	is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
\end{theorem}
	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.
	In other words, $l$-th PLS component $\xi_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.

@@

	\subsection{Proof of  Lemma \ref{lemma:cross_cov_functional} }\label{section:proof:lemma:cross_cov_functional}
	\jongmin{An alternative proof to the compactness of $\mathcal{U}$; rather than directly showing $\mathcal{U}$ is compact, we show $\mathcal{C}_{YW}$ is compact}
	\begin{proof} 
	Any bounded linear functional from a Hilbert space to  $\mathbb{R}$  is a compact operator.
	This is because the image of any bounded set under such a functional is a bounded set in $\mathbb{R}$,
	and by Bolzano-Weierstrass Theorem, every bounded sequence of real numbers has a convergent subsequence.
Therefore,  to show that $\mathcal{C}_{YW}$ is a compact operator, it suffices to show that 
 $\mathcal{C}_{YW}$ is a bounded linear functional.

\medskip
\noindent
\textit{Linearity.}~	  
 The operator $\mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathbb{R}$ is defined as 
 $\mathcal{C}_{YW} h = \langle \Sigma_{YW}, h \rangle_\mathcal{H}$.
 For any $h_1, h_2 \in \mathcal{H}$ and scalar $c \in \mathbb{R}$, the linearity of the inner product implies: \begin{align*} \mathcal{C}_{YW}(h_1 + h_2) &= \langle \Sigma_{YW}, h_1 + h_2 \rangle_\mathcal{H} = \langle \Sigma_{YW}, h_1 \rangle_\mathcal{H} + \langle \Sigma_{YW}, h_2 \rangle_\mathcal{H} = \mathcal{C}_{YW} h_1 + \mathcal{C}_{YW} h_2,
 	 \\ 
 	 \mathcal{C}_{YW}(c h) &= \langle \Sigma_{YW}, c h \rangle_\mathcal{H} = c \langle \Sigma_{YW}, h \rangle_\mathcal{H} = c \, \mathcal{C}_{YW} h. \end{align*}
 Thus, $\mathcal{C}_{YW}$ is a linear functional.

\medskip
\noindent
\textit{Boundedness.}~ 
To show that $\mathcal{C}_{YW}$ is bounded, we need to find a finite constant $M$ such that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathcal{H}$ for all $h \in \mathcal{H}$. By the Cauchy-Schwarz inequality, we have: \begin{equation*} 
	|\mathcal{C}_{YW} h| = |\langle \Sigma_{YW}, h \rangle_\mathcal{H}| \leq \|\Sigma_{YW}\|_\mathcal{H} \|h\|_\mathcal{H}. 
	\end{equation*}
Now, we must verify that $\|\Sigma_{YW}\|_\mathcal{H}$ is finite. 
Recall that 
$$\Sigma_{YW} = (\sigma_{YX,1}(t), \ldots, \sigma_{YX,K}(t), \sigma_{YZ,1}, \ldots, \sigma_{YZ,p}).$$
  Let $\mu([0,1])$ denote a Lebesgue measure of $[0,1]$, and let $T = \max_{k=1, \ldots, K} \, \mu([0,1])$.
The norm of $\Sigma_{YW}$ in $\mathcal{H}$ is given by: \begin{equation*} \|\Sigma_{YW}\|_\mathcal{H}^2 = \sum_{k=1}^K \int_0^1 \sigma_{YX,k}(t)^2 \, dt + \sum_{r=1}^p \sigma_{YZ,r}^2
	<
	K T Q_1 + p  Q_2 < \infty,
 \end{equation*} 
 where the last inequality uses the condition \eqref{condition_for_compact}.
 Let $M = \sqrt{K T Q_1 + p  Q_2 }$. Thus, we have shown that $|\mathcal{C}_{YW} h| \leq M \|h\|_\mathcal{H}$ for a finite constant $M$.
 This completes the proof of Lemma \ref{lemma:cross_cov_functional}.

@@

\section{Proof of Theorem \ref{theorem:population_PLS}}\label{section:proof:theorem:population_PLS}
 \begin{proof}
Since Proposition \ref{proposition:compact_operator} implies that $\mathcal{U}$ is compact,
by Theorem 4.3.1 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
\end{proof}
  The singular value decomposition of $\mathcal{C}_{YW}$ is given by
	\begin{equation*}
		\mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
	\end{equation*}
	Let $\Vert \cdot \Vert_{op}$ denote an operator norm. Then, applying Theorem 4.3.4 in \citet{hsingTheoreticalFoundationsFunctional2015}, we can show that
	\begin{equation*}
		\Vert \mathcal{C}_{YW} \Vert_{op} = \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} | \mathcal{C}_{YW} \mathbf{h} |^2 
		= \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} | E(\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y)|^2 
		= \sup_{\substack{\mathbf{h} \in \mathcal{H} \\ \Vert \mathbf{h} \Vert_\mathcal{H}=1}} \textnormal{Cov}^2(\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H}, Y) 
		= \kappa_1^2,
	\end{equation*}
	with maximum attained at $\mathbf{h}=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \, \circ \, \mathcal{C}_{YW} = \mathcal{C}_{WY} \, \circ \, \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\kappa_1^2.$
